# Created:    September 29, 2019
# @Student    Timothy Olugbenga Akintoye, (oakintoy@kent.edu)
# @version:   1.0
# File:       Assignment_4
# Comment:    
################################################################
#***#
#* Note that lines that start with # are comments.
#***#
##########################################################################################################################
# PURPOSE: of this assignment is to formulate and solve a transportation / transshipment problem.			 #
# Directions 														 #
# Heart Start produces automated external defibrillators (AEDs) in each of two different plants (A and B). The unit      # production costs and monthly production capacity of the two plants...The AEDs are sold through three wholesalers.        #
# The shipping cost from each plant to the warehouse of each wholesaler along with the monthly demand from each          #
# wholesaler are also indicated in the table. How many AEDs should be produced in each plant, and how should they be     #
# distributed to each of the three wholesaler warehouses so as to minimize the combined cost of production and shipping? #
#####################################################################################
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

***


```{r}
library(lpSolveAPI)
x <- read.lp("oakintoy_4 (3).lp")
x
```


```{r}
solve(x)
get.objective(x)
get.variables(x)
get.constraints(x)
get.sensitivity.objex(x)
get.sensitivity.rhs(x)
```
***