# Created:    September 22, 2019
# @Student    Timothy Olugbenga Akintoye, (oakintoy@kent.edu)
# @version:   1.0
# File:       assignment 3
# Comment:    
################################################################
***

***
* Note that lines that start with # are comments. 

```{r,eval=FALSE}
install.packages("lpSolveAPI")
library(lpSolveAPI)

```
***
Let us set up the Weigelt Corporation problem. Note that we had nine decision variables, and nine constraints.
In the first formulation, we will directly create the objective function and constraints
```{r}
# make an lp object with 0 constraints and 9 decision variables
lprec <- make.lp(0, 9)


set.objfn(lprec, c(420, 360, 300, 420, 360, 300, 420,360,300))

# change the direction to set maximization for profit
lp.control(lprec,sense='max')


# 3 constrains for Production Capacity of the three plants
add.constraint(lprec, c(1, 1, 1, 0, 0, 0, 0, 0, 0), "<=", 750)
add.constraint(lprec, c(0, 0, 0, 1, 1, 1, 0, 0, 0), "<=", 900)
add.constraint(lprec, c(0, 0, 0, 0, 0, 0, 1, 1, 1), "<=", 450)

add.constraint(lprec, c(20, 15, 12, 0, 0, 0, 0, 0, 0), "<=", 13000)
add.constraint(lprec, c(0, 0, 0, 20, 15, 12, 0, 0, 0), "<=", 12000)
add.constraint(lprec, c(0, 0, 0, 0, 0, 0, 20, 15, 12), "<=", 5000)

add.constraint(lprec, c(1, 0, 0, 1, 0, 0, 1, 0, 0), "<=", 900)
add.constraint(lprec, c(0, 1, 0, 0, 1, 0, 0, 1, 0), "<=", 1200)
add.constraint(lprec, c(0, 0, 1, 0, 0, 1, 0, 0, 1), "<=", 750)
```


```{r}
add.constraint(lprec, c(900, 900, 900, -750, -750, -750, 0, 0, 0), "=", 0)
add.constraint(lprec, c(450, 450, 450, 0, 0, 0, -750, -750, -750), "=", 0)


# To identify the variables and constraints, we can
# set variable names and names of the constraints

ColNames <- c("AP1", "AP2", "AP3", "BP1", "BP2", "BP3", "CP1", "CP2", "CP3")
RowNames <- c("production capacity P1", "Production Capacity P2", "Production Capacity P3", "in process storage P1", "in process storage P2", "in process storageP3", "A sales forecast", "B sales forecas", "C sales forecas","pl1","pl2")
dimnames(lprec) <- list(RowNames, ColNames)

# Now, print out the model
lprec

# The model can also be saved to a file
write.lp(lprec, filename = "oakintoy.1p", type = "lp")
```
We now solve the above LP problem, and output the objective function and variables
```{r}
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
```




```{r}
```


```{r}
get.sensitivity.rhs(lprec)
get.sensitivity.obj(lprec)
```



```{r}
cbind(get.sensitivity.rhs(lprec)$duals[1:11], get.sensitivity.rhs(lprec)$dualsfrom[1:11], get.sensitivity.rhs(lprec)$dualstill[1:11])

```
```{r}
cbind(get.sensitivity.rhs(lprec)$duals[12:20], get.sensitivity.rhs(lprec)$dualsfrom[12:20], get.sensitivity.rhs(lprec)$dualstill[12:20])
```
